% Other Academic Activities
\ifswedish
  \section{Övriga aktiviteter}
    \position
      {2016 \textemdash{}}
      {Översättare}
      {Planet Press}
      {Jag översätter korta vetenskapliga artiklar för barn av det European Geosciences Union (EGU) Planet Press-initiativet från engelska till spanska.}
    \position
      {2013}
      {Volontär}
      {IAHS}
      {Jag stödde organisationen av 2013 IAHS, IAPSO, IAPSEI Joint Assembly i Göteborg.}
\else
  \section{Other Activities}
     \position
      {June 2024 \textemdash{} Now} 
      {LPC Physics Forum chair}
      {Fermilab}
      {Organization of seminars for CMS and non CMS members.}
     \position
      {2022 \textemdash{} Now} 
      {ACT-SO Judge}
      {DuPage County}
      {Judge or mock judge for the Afro-Academic, Cultural, Technological, and Scientific Olympics (ACT-SO) in the Engineering category. The program targets African American High school students.}
     \position
      {2022 \textemdash{} Now} 
      {SiDet tour guide}
      {Fermilab}
      {Providing tours of the Silicon Detector facility at Fermilab for students, experts of the scientific community and other guests of the laboratory.}
      \position
      {2022 \textemdash{} 2023} 
      {LPC Events Committee member}
      {Fermilab}
      {Organization of events, workshops and tutorials.}
    \position
      {2018 \textemdash{} 2020} 
      {DESY Language Café}
      {DESY}
      {Organized bi-weekly meeting to practice different languages with the support of DOIT (Doktoranden-Initiative in partnership of DESY, Universität Hamburg \&  PIER Helmholtz Graduate School), CSSB (Centre for Structural Systems Biology) and Fortbildung DESY.}
\fi
